%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Frontier Communications$|$ }\emph{Node.js, Express.js, Fastify, Microservices, REST API's, Swagger}, MongoDB, RedisCache} 
    {}
    \resumeItemListStart
       \resumeItem{Documented \textbf{Microservices \& REST API’s} into \textbf{Swagger Doc} to efficiently used in \textbf{Business} requirements.}
        \resumeItem{Fixed \textbf{Sonar Lint / ES Lint }issues in coding standards to enhance the code quality and readability helped to \textbf{reduce 85\% bugs} and save \textbf{Debugging time and Efforts} .}
        \resumeItem{Enhanced \textbf{MongoDB and In-memory Redis cache databases} efficiency by restructuring data models and \textbf{optimizing cache} usage achieved a \textbf{35\% reduction in database latency} and a \textbf{25\% increase in overall application performance.} }
        \resumeItem{ \textbf{Maintain \& Merging} code on the Git branch to maintain the integration in the dev branch on production.}
        \resumeItem{Written \textbf{Jest framework unit test cases} for the Microservices API endpoints to ensure \textbf{85\% above Code coverage} and to make production code tested and fully functional.}
    \resumeItemListEnd
   \resumeProjectHeading
    {\textbf{APIGEE Hybrid Migration $|$ }\emph{Node.js, Express.js, APIGEE, AWS, REST API's, Axios}} 
    {}
    \resumeItemListStart
       \resumeItem{Crafted \textbf{Migration Scripts to automate} Import and Export\textbf{ APIGEE OPDK} services via \textbf{Node.Js JavaScript} Framework helped to \textbf{migrate} into Hybrid Environment with the \textbf{embedded functionality} of scripts that \textbf{generates Report} for the \textbf{production proxies} and services of APIGEE to identify \textbf{inactive Proxies} to save \textbf{cost by 40\% on Proxies}. }
        \resumeItem{Deployed migrated\textbf{ APIGEE on-PREM} services to \textbf{Google Cloud Platform} in Management Plane by using \textbf{Redhat Open Shift for AWS} on respective \textbf{Node \& Pods }present in\textbf{ VM Clusters}.}
        \resumeItem{Automated \textbf{APIGEE Sharedflows, Proxies and Target Servers} to migrate from \textbf{OPDK onPrem to APIGEE Hybrid}.}
    \resumeItemListEnd
     \resumeProjectHeading
    {\textbf{Hawlett Packard Enterprises $|$ }\emph{Java, Linux, Neo4j, Cassandra, Networking} } 
    {}
    \resumeItemListStart
        \resumeItem{Developed \textbf{Python and Shell Script} to \textbf{automate }Manual Data Updates in operations task by using \textbf{Linux and Shell Scripting} and added in the \textbf{cronjob} to save tedious efforts saves time and \textbf{improved 60\% performance.} }
         \resumeItem{O\textbf{ptimized Neo4j database} queries, reducing \textbf{page load times by 15\% }and enhancing overall application performance }
         \resumeItem{Fixed \textbf{Vunlerabilities} with \textbf{High Severity} to ensure secure access of Linux servers across the Network. }
         \resumeItem{Handling and managing all the UCA and UOC services for PAN India circle.}
         \resumeItem{End to End troubleshooting for the issues related to OSS platform, Fault Management.}

         
    \resumeItemListEnd
\resumeSubHeadingListEnd